Predicting Audio Features with Last.fm Tags

### 2023-04-24 paper/main.tex
working on intro

Music informationn retrieval (MIR) is a field that focuses on the analysis,
processing and knowledge discovery of latent information in music pieces \cite{ramirez2020machine}.

Many of the challenges in this field use audio features, such as valence and energy, to predict other music-related aspects.
For example, some studies have been using these features to predict the probably of a track being a hit [REF].

>>>>

Music information retrieval (MIR) is an interdisciplinary research field that encompasses the extraction,
processing, and knowledge discovery of information contained in music.
MIR research intersects with other fields, such as computer science, signal processing, musicology, and sociology.
The field covers applications in recommendation systems, music classification,
music source separation, and music generation, among others \cite{ramirez2020machine}.

MIR applications often attempt to extract information from the music audio signal,
but analyzing associated metadata is also a common practice.
Audio signals are typically preprocessed and transformed into intermediate formats, such as frequency-based representations.
Associated metadata, such as editorial information, lyrics, or user-generated content is usually in text format.
However, metadata can be available as images of videos, for example, when analyzing album artwork, or music videos.

Depending on the specific MIR application, researchers or practitioners expect different output values.
For example, an application that extracts audio features might return values for the tempo, the key, or the sample rate.
In more complex applications, where, for example, machine learning is used, applications might return the estimated emotion that a track produces on a listener, or the predicted music genre of a particular track.

Many of the challenges in this field use audio features to predict other music-related aspects.
Examples of these features are 
For example, some studies have been using these features to predict the probably of a track being a hit [REF].
